### 2019-06-27 README.Rmd
use real links for contributing and coc in readme

See our [CONTRIBUTING](.github/CONTRIBUTING.md) document.

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

@@

[tut]: https://ropensci.org/tutorials/taxize.html

>>>>

See our [CONTRIBUTING](https://github.com/ropensci/taxize/blob/master/.github/CONTRIBUTING.md) document.

@@

* Please [report any issues or bugs](https://github.com/ropensci/taxize/issues).
* License: MIT
* Get citation information for `taxize` in R doing `citation(package = 'taxize')`
* Please note that this project is released with a [Contributor Code of Conduct][coc].
By participating in this project you agree to abide by its terms.

@@

[tut]: https://ropensci.org/tutorials/taxize.html
[coc]: https://github.com/ropensci/taxize/blob/master/CODE_OF_CONDUCT.md
